---
title: "Data management"
author: "Math 685 students"
date: "9/20/2019"
output: 
  html_document: 
    keep_md: yes
---

# Read in data
```{r}
knitr::opts_chunk$set(echo = TRUE)
ames <- read.csv("https://norcalbiostat.netlify.com/data/ames.csv", header=TRUE)
```


# Do data management 
```{r}
library(tidyverse)
```

```{r}
str(ames)
```


```{r}
summary(ames$House.Style)
str(ames$House.Style)
```


```{r}
summary(ames$Yr.Sold)
```

```{r}
str(ames$Yr.Sold)
```


```{r}
ames %>% 
  count(Yr.Sold)
```



```{r}
ggplot(data = ames, mapping = aes(x = Yr.Sold)) +
  geom_histogram(binwidth = 0.1)
```

I am interested in looking at the trends of the year the house was sold and the sale price. By doing a str on the data set, those two variables are integers. 

```{r}
ggplot(data = ames, mapping = aes(x = SalePrice)) +
  geom_histogram(binwidth = 100000)
```
Checking if there are unusual values

```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(ylim = c(0, 800))
```


```{r}
ames %>% 
  count(SalePrice)
```

```{r}
summary(ames$SalePrice)
```


```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(ylim = c(0, 1000))
```

```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(xlim = c(800000, 500000))
```

I don't think there are any unusual values that need to be removed or coded as missing, but if someone wanted to double check that would be great. 

```{r}
summary(ames$Yr.Sold)
```


```{r}
str(ames)
```


```{r}
ggplot(data = ames, mapping = aes(x = SalePrice, colour = Yr.Sold)) +
  geom_freqpoly(binwidth = 100000)
```


```{r}
ggplot(data = ames, mapping = aes(x = Yr.Sold, colour = SalePrice)) +
  geom_freqpoly(binwidth = 0.1)
```

```{r}
ggplot(data = ames, mapping = aes(x = SalePrice, colour = Yr.Sold)) +
  geom_freqpoly(binwidth = 100000)
```


```{r}
ames %>% group_by(Yr.Sold) %>% 
         summarise(mean=mean(SalePrice), 
                   sd = sd(SalePrice))
```


Let's see if there is a trend in the year the houses were sold and the sale price. 
```{r}
ggplot(ames, aes(x=SalePrice, fill=Yr.Sold)) + 
    geom_histogram() + 
    facet_wrap(~Yr.Sold)
```
I like this set of graphics best so far, but I am still not sure if this is clear on what I am looking at. 

```{r}
ggplot(ames, aes(x=SalePrice, fill=Yr.Sold)) + 
    geom_histogram() + 
    facet_wrap(~Yr.Sold)+
  geom_freqpoly(binwidth = 10000)+
  coord_cartesian(xlim = c(0, 550000))
```
I think setting a binwidth is what I want to do to make it more clear, but I am not sure what to set it at. I have played around with different numbers and so far 10,000 looks the best. Any suggestions here?
 
```{r}
ggplot(ames, aes(x=SalePrice, col=Yr.Sold)) + geom_density()
```
I don't think this one makes any sense.

```{r}
ggplot(data = ames, mapping = aes(x = Yr.Sold, y = SalePrice)) +
  geom_boxplot()
```



```{r}
ames_clean <- ames
```


# Save clean data
```{r}
save(ames_clean, file = "ames_clean.Rdata")
```



