---
title: "Data management"
author: "Math 685 students"
date: "9/20/2019"
output: html_document
---

# Read in data
```{r}
knitr::opts_chunk$set(echo = TRUE)
ames <- read.csv("https://norcalbiostat.netlify.com/data/ames.csv", header=TRUE)
```


# Do data management 
```{r}
library(tidyverse)
```

```{r}
str(ames)
```
```{r}
summary(ames$House.Style)
str(ames$House.Style)
```
```{r}
summary(ames$Yr.Sold)
```
```{r}
ggplot(data = ames, mapping = aes(x = Yr.Sold)) +
  geom_histogram(binwidth = 0.1)
```

I am interested in looking at the trends of the year the house was sold and the sale price. By doing a str on the data set, those two variables are integers. 

```{r}
ggplot(data = ames, mapping = aes(x = SalePrice)) +
  geom_histogram(binwidth = 100000)
```
Checking if there are unusual values

```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(ylim = c(0, 800))
```
```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(ylim = c(0, 1000))
```

```{r}
ggplot(ames) + 
  geom_histogram(mapping = aes(x = SalePrice), binwidth = 100000) +
  coord_cartesian(xlim = c(800000, 500000))
```

I don't think there are any unusual values that need to be removed or coded as missing, but if someone wanted to double check that would be great. 


```{r}
summary(ames$Yr.Sold)
```


```{r}
str(ames)
```
```{r}
ggplot(data = ames, mapping = aes(x = SalePrice, colour = Yr.Sold)) +
  geom_freqpoly(binwidth = 100000)
```
```{r}
ggplot(data = ames, mapping = aes(x = Yr.Sold, colour = SalePrice)) +
  geom_freqpoly(binwidth = 0.1)
```



# Save clean data
```{r}
#save(clean, "ames_clean.Rdata")
```



